% TODO: Add a picture of each project here
\section{Proje\textcolor{mycolor}{cts}}
  \subsection{Home server with linux}

  Designed my personal home server including all personal projects \& services, with best practices in mind.
    
  \begin{itemize}
    \item Configured and maintained a home server running multiple Docker services, including web applications, databases, and media servers.
    \item Set up and managed a personal Docker swarm cluster on a home server, utilizing Docker Compose for efficient service deployment and management.
    \item Implemented a containerized home automation system using Docker, integrating various IoT devices and services into a cohesive platform.
  \end{itemize}

  \subsection{Robotic arm that plays connect 4}
    This a project for the last year of high school where me and another student created a robotic arm that plays connect 4.
    My part of the project was writing movements for the arm and 3D printing parts.
    The other student wrote the AI for the arm.
    \subsubsection{Duration}
      0.5 year.

%\vspace{2cm}

  \subsection{3D Printer}
    I have a Ender 3 V2 at my personal workspace. This serves as a platform for my creative and technical endeavors. My proficiency extends to designing and fabricating intricate parts and prototypes, showcasing a keen eye for detail and a deep understanding of 3D printing technology.
    \vspace{.55em}
    \par
    \subsection{Resume}
    This project involved the meticulous creation of a professional resume using LaTeX, 
    a document preparation system renowned for its precision and high-quality typesetting. 
    The resume design emphasizes clarity and aesthetic appeal, 
    showcasing LaTeX's ability to produce complex and well-structured documents. 
   