\section{Work Experie\textcolor{mycolor}{nce}}
\subsection{iDalko - Premium Atlassian Partner}
\vspace{.55em}

Student Intern at {\href{https://www.idalko.com}{iDalko}}.{\textcolor{mygrey}{\hspace*{\fill}Februari 2022 - may 2022}}
\vspace{.55em}
\begin{flushleft}
\par
I developed a tool in \textcolor{mycolor}{Javascript} for non-technical people to provision and setup user accounts during the on-cross and off-boarding steps. This ensured an automated setup of privileges between our different internal systems.
This tool was designed to integrate into our Atlassian ecosystem such that HR and other departments could simplify the process.
It was created using \textcolor{mycolor}{Angular, node.js, express, docker, Atlassian plugin system} and other technologies.
\vspace{.55em}
\par
\textbf{User-Centric Design}
Tailored for individuals without a technical background, the tool was designed to be intuitive, ensuring ease of use and effective navigation.
\vspace{.55em}
\par
\textbf{Automated Privilege Management}
I incorporated features that automated the assignment of user privileges across our diverse internal systems, minimizing manual intervention and potential errors.
\vspace{.55em}
\par
\textbf{Integration with Atlassian}
To ensure a cohesive user experience, I integrated the tool into our existing Atlassian ecosystem. This facilitated a smoother transition and allowed various departments, including HR, to benefit from its capabilities.
\vspace{.55em}
\par
\textbf{Enhanced Cross-Departmental Collaboration}
By simplifying and automating the on-boarding and off-boarding processes, the tool fostered better collaboration and efficiency across different teams within the organization.
\end{flushleft}
Junior System Engineer at {\href{https://www.idalko.com}{iDalko}}.{\textcolor{mygrey}{\hspace*{\fill}June 2022 - August 2023}}
\vspace{.55em}
\begin{flushleft}
\par
\textbf{Endpoint Security}
Implemented and oversaw Cortex XDR operations, safeguarding our systems against potential threats.
\vspace{.55em}
\par
\textbf{Identity and Access Management}
Integrated Single Sign-On (SSO) solutions using protocols such as SAML and OIDC, providing seamless and secure access for all users.
\vspace{.55em}\par
\textbf{Mobile Device Management}
Spearheaded the deployment and management of mobile devices using platforms like ABM, Miradore, and Mosyle, ensuring a productive and secure mobile workforce.
\vspace{.55em}
\par
\textbf{Linux System Administration}
Directly manage comprehensive Linux system tasks, including regular updates, Docker container operations, system migrations, patch applications, and timely backups.
\vspace{.55em}
\par
\textbf{Infrastructure Automation}
Championed Infrastructure as Code (IaC) and implemented automation strategies using Ansible, streamlining operations and bolstering infrastructure reliability.
\vspace{.55em}
\par
\textbf{user Management}
Oversee user provisioning and access management, ensuring optimal system integrity and security.
\vspace{.55em}
\par
\textbf{Web Development}
Built and maintained web applications using Angular and Node.js, demonstrating proficiency in both infrastructure management and software development.
\vspace{.55em}
\end{flushleft}

